### 2018-08-30 README.Rmd
update readmes with github_markdown_nested format
update readme with guidelines

---
output: github_document
editor_options: 
  chunk_output_type: console
---

@@

```{r child='scripts/README.Rmd'}
```

@@

>>>>

---
output: dynbenchmark::github_markdown_nested
editor_options: 
  chunk_output_type: console
---

@@

```{r results = 'asis'}
knit_nest("scripts")
```

@@

## Guidelines

Based on the results of the benchmark, we provide context-dependent user guidelines. If you want to run methods based on these guidelines, see the [dynorepository](https://github.com/dynverse/dyno). For the guidelines itself, see the [dynguidelines ](https://github.com/dynverse/dynguidelines).
